A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-09-08 Review/response_strategy.Rmd

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 300px;
}

pre, code {white-space:pre !important; overflow-x:scroll !important}

.question {
  text-align: justify;
}

.response{
  color: #145805;
  text-align: justify;
  margin-bottom: 30px;
}

.response_strategy {
  color: #000080;
  text-align: justify;
  margin-bottom: 30px;
}

.rouge {
  color: red;
  text-align: justify;
  margin-bottom: 30px;
} 
```

@@

# Reviewer 1

::: question
In the manuscript 'A hierarchical model to evaluate pest treatments from prevalence and intensity data', Favrot & Makovski present a new and welcome (Bayesian) method for the (meta-)analysis of countable 'infection' units on individual hosts, where the recorded variable may be either the proportion of 'infected' hosts (prevalence) or the mean number of infection units per individual host (intensity), or both quantities. Then, a simulation study is used to demonstrate that intensity data provide more accurate estimates than prevalence data (especially for abundant 'infections'), and to assess the accuracy of the estimates depending on the number of trials. The provided code and convergence seems good. 
:::

::: question
Before starting my comments, I wish to apologize deeply for the inconvenience caused to the authors and editor by the time taken to review the manuscript. Besides, I did not find any line numbering; thus, my comment below only vaguely refer to paragraph or page numbers.
:::

::: response_strategy
Ajouter des numéros de lignes dans mes fichiers.
:::

@@

::: question
A general comment : the article focusses on aphid abundance on plants sampled during field trials designed to compare the efficacy of various pest control options, but the framework is more generic (and might be used e.g. in animal/human epidemiology) and the authors may highlight this point in the abstract, introduction and/or discussion.
:::

::: response_strategy         
Ajouter une phrase dans la conclusion pour souligner ce point.
:::

::: response
We added the following sentece in the conclusion : 
:::

@@

## Major comments

::: question
My only methodological comment relates to the choice of a Poisson distribution for W, which is the number of aphids on each plant. Because aphids land and initiate exponentially growing clonal populations at different times on different plants of the same trial x treatment x block x time combination, W should have an overdispersed Poisson distribution (e.g., negative binomial), instead of a Poisson distribution (eq. 1). Thus, Y (the sum of N independent W variables) should not have a Poisson distribution (eq. 3). It would be interesting to test whether an overdispersed Poisson distribution is better than a Poisson distribution for fitting the unaggregated data on the number of aphids on each of the N_i (i.e. 10 here) sampled plants (gaining statistical power from the multiple trials). Although the authors state (in part 2.1) that such data are not available to the authors, these raw data are classically recorded and might be provided by the unspecified colleagues who conducted the field trials (by the way, the institutions that performed the field trials should be mentioned more explicitly).
:::

::: response_strategy         
Ce commentaire remet en question le modèle que l'on utilise et propose d'en utiliser un autre : la négative binomiale. La négative binomiale permet de gérer la surdispersion. Ce commentaire nous a fait remarquer que nous n'avions pas vérifié l'ajustement aux données de notre modèle. La première étape sera donc de faire cette vérification. On la fera en appliquant la méthode du "posterior predictive checking", qui consiste, pour chaque observation, à calculer la probabilité que le modèle propose une valeur plus extrême que celle de l'observation considérée. On fera cette vérification uniquement sur les données réelles. La seconde étape sera de coder le modèle reposant sur la loi négative binomiale et de le comparer au modèle de Poisson en utilisant le posterior predictive checking : on fera un scatter plot des proba à posteriori de dépasser les valeurs extrêmes selon les deux modèles (probas d'un modèle en abscisse et probas de l'autre en ordonné).

@@

Le modèle est donné par

$$
    W_{ijkts}\sim\mathcal{NB}\big(r,\ \lambda_{ijkt}\big)
$$

Where $\lambda_{ijkt}$ is the mean of $W_{ijkts}$ and $r$ is the overdispersion parameter. The model on $\lambda_{ijkt}$ is the same as the one of the Poisson model, but without the term $\epsilon_{ijkt}$ :

$$\log\ \lambda_{ijkt} = \alpha_0 + \beta_{0i} + \gamma_{0j}  + (\alpha_1 + \gamma_{1j})\ X_t + u_{ij}$$

@@

        MSE_poisson = sum((c(alpha_0 + log(S), gamma_0[- 1], alpha_1, gamma_1[- 1]) - summary(res_Poisson)$coefficients[, 1]) ^ 2)

        MSE_NegB = sum((c(alpha_0 + log(S), gamma_0[- 1], alpha_1, gamma_1[- 1]) - summary(res_negB)$coefficients[, 1]) ^ 2)

        res = rbind(res, data.frame(I = I,
                                    seed = seed,
                                    Model = c("Poisson with OLRE", "Negative binomiale"),
                                    MSE = c(MSE_poisson, MSE_NegB),
                                    Message = c(summary(res_Poisson)$optinfo$message,
                                                summary(res_negB)$optinfo$message),
                                    Warning = c(summary(res_Poisson)$optinfo$warnings %>% length,
                                                summary(res_negB)$optinfo$warnings %>% length)))
    }
}
```

```{r}
ggplot(res) +
    geom_boxplot(aes(y = MSE, x = factor(I), fill = Model))
```
:::

@@

## Minor comments

My other comments are minor and mainly concern typos:

- &#10060; p.3 l.2: 'indeed more time-dependent'

::: response_strategy
Ce commentaire fait référence à cette phrase (dans l'introduction) : "measuring intensity is indeed often more time demanding than measuring prevalence, in particular when the pest individuals are small, numerous, and difficult to detect." Je ne comprends pas ce commentaire.
:::

@@

- &#9989; p.3: 'negative impact on a wide range', 'this family of pesticides has been banned', 'some trials may report'

  - &#9989; 'negative impact on a wide range'

  ::: response_strategy
  fait référence à la phrase : "Recently, neonicotinoids were recognized as presenting high risks for the environment with a negative impact a wide range of non-target organisms"

@@

  =\> on a oublié le "on", corriger
  :::

  - &#9989; 'this family of pesticides has been banned'

  ::: response_strategy
  fait référence à la phrase : "and this familly of pesticides had been banned in several European countries"

@@

  =\> erreur de temps, changer had par has
  :::

  - &#9989; 'some trials may report'

  ::: response_strategy
  fait référence à la phrase : "Consequently, for a given pest treatment, some of trials may report prevalence data while others report intensity data"

@@

  =\> le "of" est en trop, corriger
  :::

- &#9989; p.3: 'both types of data', replace 'will' with 'may' (twice)

  - &#9989; ‘both types of data’

  ::: response_strategy
  fait référence à la phrase : "while others report intensity data or both type of data"

@@

  => il manque un “s” à “type”, corriger
  :::

  - &#9989; replace ‘will’ with ‘may’ (twice)

  ::: response_strategy
  les deux will en questions sont dans la phrase suivante : "It is unclear whether the simultaneous analysis of prevalence and intensity data will increase the accuracy of the estimated treatment efficacy compared to the use of a single type of data, and whether this will increase the probability of identifying the most efficient treatments" =\> faire le remplacement
  :::

@@

- p.3-4: please rephrase this sentence for clarity

::: response_strategy
Le reviewer fait référence à cette phrase : "Based on simulations, we then quantify the reduction of mean absolute errors in the estimated treatment efficacies induced by the combination of prevalence and incidence data compared to the use of a single type of data."

@@

**Proposition de reformulation** : "Based on simulations, we then quantify the reduction of mean absolute errors in the estimated treatment efficacies induced by using both prevalence and intensity data, compared to the use of exclusively either prevalence or intensity data."
:::

- &#9989; 2.1: 'the Netherlands', 'Intensity and prevalence were monitored at different times after treatments'

  - &#9989; 'the Netherlands'

  ::: response_strategy
  fait référence à la phrase : "Data were collected in 32 field trials conducted in France, Belgium and Netherlands to compare several treatments"

@@

  =\> oubli du "the", corriger
  :::

  - &#9989; 'Intensity and prevalence were monitored at different times after treatments'

  ::: response_strategy
  fait référence à la phrase : "Intensity and prevalence were monitored at different dates during the growing season."

@@

::: response_strategy
=\> supprimer ces deux phrases
:::

- &#9989; p.6: 'assuming the Ws are independent', 'quantities used in the model'

  - &#9989; ‘assuming the Ws are independent’

  ::: response_strategy
  fait référence à la phrase : "Then, assuming the Ws independent, we have:"

@@

  =\> rajouter "are"
  :::

  - &#9989; ‘quantities used in the model’

  ::: response_strategy
  fait référence à la phrase : "The different quantities used by the model are defined in Table 1."

@@

  =\> changer "by" par "in"
  :::

- p.6: a more precise description of model parameterisation is necessary: does the number of sampled plants vary (only) from trial to trial (if yes, subscript i is OK)?

::: response_strategy
Oui le nombre de plantes échantillonnées ne varie que selon les essais.

@@

Pour alpha_1, la définition que l'on a dans la tables 1 est : "growth parameter of the number of pest individuals for the untreated group"

Je propose à la place : "mean growth parameter of the number of pest individuals for the untreated group (over trials and blocks)"
:::

- Isn't gamma_1j the treatment effect only at t0?

::: response_strategy
Je ne comprends pas ce commentaire, mais il m'a fait voir que la définition du temps n'est pas claire, je propose de remplacer X_t par t

@@

A revoir, il faudrait peut être dire que t=0 peut correspondre soit à la moyenne des temps de mesure, soit au jour du traitement, qu'on peut le définir comme le temps de référence, auquel cas il faut adapter la définition de alpha, il faut aussi que je vérifie qu'il n'y a pas de temps négatif, auquel cas il faudrait mettre des indicatrices dans le modèle
:::

- &#9989; 2.2.2: 'using Bayesian inference', 'to facilitate convergence'

  - &#9989; 'using Bayesian inference'

  ::: response_strategy
  fait référence à la phrase "The model parameters were estimated using a Bayesian inference with a Markov chain Monte-Carlo method."

@@

  => supprimer le "a"
  :::

  - &#9989; 'to facilitate convergence'

  ::: response_strategy
  fait référence à "and we centered the time variable $t$ to facilitate the convergence."

@@

  => supprimer le deuxième "the"
  :::

- &#9989; p.7: 'extract of the real dataset', 'likelihood'

  - &#9989; 'extract of the real dataset'

  ::: response_strategy
  fait référence à "The following code presents the inference on an extract fo the real 
dataset" dans un commentaire de code

@@

  => remplacer "fo" par "of"
  :::

  - &#9989; 'likelihood'

  ::: response_strategy
  fait référence à "Likelyood" dans le modèle jags
   => remplacer le "y" par un "i"
  :::

@@

- p.11 and thereafter: why 974 replicates in the simulation study and not, e.g., 1000? Did some replicates fail? Yes, some replicates failed with jags, and due to the computation time, we did not restart the calculations. Should we to it ?

- &#9989; p.12: 'As the computing time is growing', 'Our simulation results'

  - &#9989; 'As the computing time is growing'

  ::: response_strategy
  fait référence à "As the calculus time is growing fast" dans un commentaire du code des simulations

@@

  => remplacer calculus par computing
  :::

  - &#9989; 'Our simulation results'

  ::: response_strategy
  faité référence à "Our simulations results are obtained" dans le même commentaire.

@@

  => supprimer le "s" de "simulations"
  :::

- &#9989; p.24 l.2: 'identifying'

  ::: response_strategy
  fait référence à "for assessing the efficacy of treatments and indentifying"

@@

  => supprimer le premier "n"
  :::

- &#9989; p.26: 'thousands', 'intensity data led to a substantial'

  - &#9989; 'thousands'

  ::: response_strategy
  fait référence à "and convergence was quickly achieved after a few thoushands iterations."

@@

  => supprimer le deuxième "h"
  :::

  - &#9989; 'intensity data led to a substantial'

  ::: response_strategy
  fait référence à "intensity data let to a substantial reduction of the uncertainty"

@@

[1] https://www.sciencedirect.com/science/article/abs/pii/S0165176500002251 Gurmu, Shiferaw, and John Elder. "Generalized bivariate count data regression models." Economics Letters 68.1 (2000): 31-36.

[2] https://link.springer.com/article/10.1007/s00180-018-0828-5#ref-CR24 Osiewalski, Jacek, and Jerzy Marzec. "Joint modelling of two count variables when one of them can be degenerate." Computational Statistics 34 (2019): 153-171.

[3] https://journals.sagepub.com/doi/abs/10.3141/2019-01?journalCode=trra Park, Eun Sug, and Dominique Lord. "Multivariate Poisson-lognormal models for jointly modeling crash frequency by severity." Transportation Research Record 2019.1 (2007): 1-6.
:::

::: response_strategy         
=> Lire ces articles et voir si on peut y faire référence dans l’introduction
:::

@@

### B.

::: question
The reason why it does make sense to consider some parameters as fixed and others as random is not very clear to me. It is stated, that this model was validated in another study (Laurent et. al 2023). As far as I can tell the main focus of the Laurent et. al 2023 was not to validate this model. I think a few high-level explanations would ease reading. It would also be usefull to cite in which sections/paragraphs of Laurent et. al 2023 equation (2) is validated.
:::

::: response_strategy
Ce commentaire fait référence à la partie suivante :
:::

@@

- $\beta_{0i}\sim\mathcal{N}(0, \sigma_0^2)$
- $u_{ij}\sim\mathcal{N}(0, \chi^2)$
- $\epsilon_{ijkt}\sim\mathcal{N}(0,\eta^2)$

*The random variables are all assumed independent. The combination of fixed and random effects used in Equation 2 has been validated in a previous study (Laurent et al. (2023)).*

The observed variables (intensity and prevalence) can be expressed as a function of $W$. We note: ...

::: response_strategy
paramètre lié au site qui sont random, on ne veux pas faire d'inférence site par site, on veut faire une inférence pour la population de site, globale, choix qui dépend de l'obejctif de l'inférence, par rapport à la population de site

@@

#### D.0.

As stated in the paper "the prevalence data are usually more accessible in practice and the intensity data more costly".

To better compare and discuss the results it would be important to get a sense of these costs. For example, if it is 10 times more costly to get Y for one trial then comparing [50% Y - 0% Z] to [0% Y - 50% Z] does not seem exactly fair.

::: response_strategy

On ne connait pas le coût d'un essai où l'on mesure Y et le coût d'un essai où l'on mesure Z, on ne peut donc pas savoir quels scénarios considérer pour faire une comparaison sur la base des coûts. Le fait de comparer [50% Y - 0% Z] et [0% Y - 50% Z] montre simplement que la mesure de Y apporte plus de précision dans l'estimation que la mesure de Z (à nombre d'observations égale).

Cependant ce commentaire me fait voir qu'il y a un problème dans l'article : la partie 3.2.3 "Is it better to measure intensity or prevalence in new pest surveys ?". Je pense que pour bien répondre à cette question il faudrait connaitre les coûts des différents scénarios.

=\> Pour moi ce n'était pas le but de l'article d'approfondir cette question du coût et de l'optimisation qui en découle, étant donné que l'on a pas cette information. En fait je pense que ça pourrait faire partie d'une limite de l'article dont on parlerait dans la conclusion. Stratégie de réponse : en parler dans la conclusion.

@@

#### D.1. &#9989;

::: question
In table 2 and 3, I think it would be clearer to always specificy the amount for Y and Z. For example [100% Y - 0% Z], [50% Y - 0% Z], ...

For now, I am not exactly sure which datasets are considered. This might explain some of the other questions I have…
:::

::: response_strategy         
=> faire la modification proposée
:::

::: response 
We made the change, it correspond to the commit "change in notation for scenarios" (dfbaa65).
:::

::: rouge
Ne faudrait-il pas en plus normaliser la notation de la façon suivante : toujours Y en premier et Z en deuxième. Exemple "50% Y - 0% Z", "0% Y - 50% Z", plutôt que "50% Y - 0% Z", "50% Z - 0% Y".
:::

@@

#### D.2.

::: question
I am not sure I understand the choice of the 4 subdatasets in table 2. Would it not make sense to consider all the scenarios of table 3? In particular why not [100% Y - 100% Z] and [0% Y - 100% Z]?
:::

::: response_strategy         
Expliquer que ce n'est pas possible car on ne dispose des Z que dans 15 essais sur les 32 (paragraphe 2.1)
:::

::: response
We could not consider all the scenarios defined in Table 3 for the real data because we only have data for Z in 15 out of the 32 trials (see paragraph 2.1, "The number of infested plants (prevalence) was measured as well, but only in 15 trials out of 32"). Therefore, we were unable to consider the scenarios "100% Z - 0% Y," "100% Y - 100% Z," and "100% Z - 50% Y." We also did not consider the scenario "100% W" because W is not measured (only the sum of aphids on the N sugar beets in the sample is reported).
:::

::: question
Based on D0) why not consider more intermediate levels of Y : [25%Y - 100% Z], ...
:::

::: response_strategy
Expliquer que l'objectif n'était pas de faire une optimisation de design, rajouter une phrase quelque part pour souligner que notre modèle pourra être utiliser pour faire de l'optimisation de design.
:::

::: response
We did not consider more intermediate scenarios because our goal was not to perform an experimental design optimization but simply to demonstrate that it is possible to combine Y and Z and that it is advantageous to do so when only Z is measured in certain trials.

To emphasize one of the benefits of our model being experimental design optimization, we have added the following sentence:
:::

::: rouge
Rajouter une phrase pour dire que notre modèle pourra être utilisé pour faire de l'optimisation de design.
:::

@@

### E.

::: question
As I already stated I am not an expert at modeling this type of data, but it feels that the number of plants is an important parameter. The larger it is the better the Z variable should be? I am not sure why this is not considered in the simulations.
:::

::: response_strategy         
Je ne suis pas sur que le nombre de plantes soit un paramètre important. Mon intuition est qu'il est équivalent au nombre de sites. Par exemple je pense que deux sites où on mesure Z sur 20 plantes est équivalent à 4 sites où on mesure Z sur 10 plantes. Le nombre de plantes N pourrait cependant faire partie d'un problème d'optimisation sous contraintes dans lequel on veut par exemple un minimum de site pour couvrir un nombre suffisant de situation environnemental (météo, composition de la terre, présence de pucerons, ...).

### 2023-09-08 Review/response_strategy.Rmd

On pourrait par exemple, étant donné $N_Y$ la taille d'échantillon pour laquelle on mesure l'intensité, chercher $N_Z$ la taille d'échantillon pour laquelle on mesure la prévalence qui soit telle que la précision obtenue avec l'intensité soit égale à la précision obtenue avec la prévalence.

Faire à peu près la même réponse que pour D.2.2 : expliquer que l'objectif n'était pas faire de l'optimisation de design, mais que cela est possible en particulier en considérant N comme un paramètre à optimiser. Rajouter une phrase quelque part pour en parler.
:::

@@

::: question
In terms of experimental design, depending on the cost of $Y$ and $Z$, increasing the number of plants (rather than measuring the intensity) might very well be a better option?
:::

::: response_strategy         
Oui, voir la réponse précédente, il doit exister un $N_z = f(N_y)$ tel que la précision obtenue avec $Y$ soit égale à celle obtenue avec $Z$.

@@

Stratégie de réponse : proposer d’en parler dans la conclusion
:::

### F.

::: question
I imagine one reason to consider a limited number of scenarios is computationnal runtime? If so, this should be stated?
:::

::: response_strategy         
=\> Oui, stratégie de réponse : parler du temps de calculs pour justifier le nombre limité de scénarios considérés
:::

@@

### G.

::: question
For section 3.1.2, when discussing the size of the credibility intervals in Figure 4. As far as I understand the conclusions are based on one subsample of the whole data, is it? If so, I think subsampling should be repeated, to argue that in general (that is over a large number of subsamples) the credibility intervals are smaller with a particular sub-dataset ([50% Y - 0 % Z], [0% Y - 50 % Z]....)
:::

::: response_strategy         
=\> Oui, ces résultats sont basés sur un seul extrait du jeu de données

@@

**Points listed in the github issue :**

- availability of the experimental data (e.g. from a zenodo repository)

- &#9989; the code to reproduce all figures in the paper (including Fig 1) should be provided

::: response_strategy
done, j'ai mis les données nécessaire aux figures dans /data/
cf commit "Point 2 of the reproducibility issue on github - adding code for Fig1" (20baac3981175f2692234ae65d58b14eb87504fa)
:::

@@

::: rouge
il faudra que je mette toutes les données extérieures dans data ? revoir le dossier Files_for_code ?
:::

- the results presented in tables should be generated from the output files (e.g. usign knitr::table)

::: response_strategy
J'ai fait ça pour les tables 4, 5, 6 et 7. 
:::

@@

::: rouge
Problème : le symbole "%" ne passe pas dans les titres (cela concerne les figures 4 et 5)
:::

- &#9989; the R package renv should be used in order to ensure the reproducibility of the envirionment used to generate your results

::: response_strategy
done, j'ai juste installer le package renv et j'ai exécuté la commande renv::init() à la racine du dossier mysubmission.
cf commit "Point 4 of the reproducibility issue on github - using renv", (831c82945dd6ce21fa88b861ea24ca9eb3a244b6)
:::

@@

- &#9989; rather than copying source code from the R package 'coda' in (https://github.com/armandfavrot/mysubmission/blob/master/Files_for_code/Functions.R), please use the package functions directly (only gelman.plot2 should remain)

::: response_strategy
cf commit "Points 5 and 6 of the reproductibility issue on github" (3c13239edfa017f6deac8feb6110d8b257542121) sur la branche correction_2.

@@

J'ai dû garder le code source de certaines fonctions du package 'coda' (fonctions non disponible avec "library(coda)"). J'ai mis l'ensemble de ces fonctions dans /functions/gelman.R (source : https://rdrr.io/cran/coda/src/R/gelman.R).
:::

- &#9989; in order to ensure that the same code has been used in the examples given in the article (chunks 'inference_example_real_data' and 'simulations'), please
  - store this code in external files (funtions in a subfolder 'functions')
  - include these files from the article source
  - add to the repository scripts to reproduce the full analysis (e.g. in a subfolder 'scripts'

::: response_strategy
cf commit "Points 5 and 6 of the reproductibility issue on github" (3c13239edfa017f6deac8feb6110d8b257542121) sur la branche correction_2
:::

### 2023-09-08 Review/response_strategy.Rmd

::: response_strategy         
Je ne suis pas sur que le nombre de plantes soit un paramètre important. Mon intuition est qu'il est équivalent au nombre de sites. Par exemple je pense que deux sites où on mesure Z sur 20 plantes est équivalent à 4 sites où on mesure Z sur 10 plantes. Le nombre de plantes N pourrait cependant faire partie d'un problème d'optimisation sous contraintes dans lequel on veut par exemple un minimum de site pour couvrir un nombre suffisant de situation environnemental (météo, composition de la terre, présence de pucerons, ...). See [here](#optimisation) .

On pourrait par exemple, étant donné $N_Y$ la taille d'échantillon pour laquelle on mesure l'intensité, chercher $N_Z$ la taille d'échantillon pour laquelle on mesure la prévalence qui soit telle que la précision obtenue avec l'intensité soit égale à la précision obtenue avec la prévalence.

Faire à peu près la même réponse que pour D.2.2 : expliquer que l'objectif n'était pas faire de l'optimisation de design, mais que cela est possible en particulier en considérant N comme un paramètre à optimiser. Rajouter une phrase quelque part pour en parler.
:::

::: response
Yes, the larger N is, the more informative Z becomes, and N could effectively be a part of an experimental design optimization problem. As mentioned in our response to comment D.2., our objective here was not to conduct an optimization of the design. However, we do propose to address this in the conclusion, and we have added the following sentence to it:
:::

::: rouge 
Ajouter la phrase en question
:::

@@

::: question
In terms of experimental design, depending on the cost of $Y$ and $Z$, increasing the number of plants (rather than measuring the intensity) might very well be a better option?
:::

::: response_strategy         
Oui, il doit exister un $N_Z$ fonction de $N_Y$, $N_Z = f(N_Y)$, tel que la précision obtenue avec $Y$ soit égale à celle obtenue avec $Z$. Il faudrait ensuite comparer le coût entre mesure de Y sur $N_Y$ betteraves et mesure de $Z$ sur $N_Z$ betteraves pour déterminer la meilleure option.

Rajouter une phrase dans la conclusion pour souligner ce point.
:::

::: response         
Yes, there must exist an $N_Z$ that is a function of $N_Y$, where $N_Z = f(N_Y)$, such that the precision obtained with $Y$ is equal to that obtained with $Z$. Then, it would be necessary to compare the cost between measuring Y on $N_Y$ sugar beets and measuring $Z$ on $N_Z$ sugar beets to determine the better option.

We have added the following sentence to the conclusion to emphasize this point:
:::

### 2023-09-08 Review/response_strategy.Rmd

We have added the following sentence to the conclusion to emphasize this point:
:::

### F.

::: question
I imagine one reason to consider a limited number of scenarios is computationnal runtime? If so, this should be stated?
:::

::: response_strategy         
Oui, stratégie de réponse : parler du temps de calculs pour justifier le nombre limité de scénarios considérés, en profiter pour citer migale.
:::

::: response
Yes, we have added the following sentence at the end of section 2.2.3 (Material and Method / Model / Simulations):
"These simulations required a significant amount of computation time and were conducted on the INRAE MIGALE server."

And we have removed the following sentence from the note associated with the code on simulations :
"We used the Migale server from INRAE to run these simulations".
:::

::: rouge
Ajouter les phrases, rajouter la citation de Migale 
:::

### 2023-09-09 Article/Article.qmd
R2 F - add sentence relative to the computation time of the simulations
R2 minor comment c - correction de la dernière phrase de l'avant dernier paragraphe de la partie 2.2.2

\
In practice, it is common that only $Y$ or $Z$ data are available in some of the trials. In this case, the resulting dataset includes observations of $Y$ in some trials and observations of $Z$ in others. The dataset may even include one type of observations only, either $Y$ or $Z$, in all trials. Here, we define four scenarios with contrasted levels of $Y$ and $Z$ availability in order to evaluate the consequences of using different types of datasets. We consider four datasets including trials with observations of $Y$, with observations of $Z$, or with both types of observation in different proportions (Table 2). The dataset "100% Y - 0% Z" includes Y data collected in the 32 trials. The dataset "50%Y" includes Y data collected in the 17 trials for which no Z observation is available. The dataset "50% $Z$" includes the Z data collected in the 15 trials for which Z observations are available. The dataset "50% $Y$ - 50% $Z$" includes $Y$ data collected in 17 trials and $Z$ data collected in the other 15 trials. The later dataset does include any trial reporting both $Y$ and $Z$ data.

@@

The code used to perform the simulations is presented below.

@@

Our simulation results are obtained by running this code for I = 10, 20, 40, 80, for all seeds between 0 and 999, with a number of adaptations and iterations equal to 36000. We used the Migale server from INRAE to run these simulations.
:::

>>>>

\
In practice, it is common that only $Y$ or $Z$ data are available in some of the trials. In this case, the resulting dataset includes observations of $Y$ in some trials and observations of $Z$ in others. The dataset may even include one type of observations only, either $Y$ or $Z$, in all trials. Here, we define four scenarios with contrasted levels of $Y$ and $Z$ availability in order to evaluate the consequences of using different types of datasets. We consider four datasets including trials with observations of $Y$, with observations of $Z$, or with both types of observation in different proportions (Table 2). The dataset "100% Y - 0% Z" includes Y data collected in the 32 trials. The dataset "50%Y" includes Y data collected in the 17 trials for which no Z observation is available. The dataset "50% $Z$" includes the Z data collected in the 15 trials for which Z observations are available. The dataset "50% $Y$ - 50% $Z$" includes $Y$ data collected in 17 trials and $Z$ data collected in the other 15 trials. The latter dataset does not include any trial reporting both $Y$ and $Z$ data.

@@

These simulations required a significant amount of computation time and were conducted on the INRAE MIGALE server. The code used to perform them is presented below.

@@

Our simulation results are obtained by running this code for I = 10, 20, 40, 80, for all seeds between 0 and 999, with a number of adaptations and iterations equal to 36000.
:::
